Computing likelihoods under the SMC for a general class of ARGs.

### 2025-02-20 paper.tex
remove equation for mutations
Closes #20

an not considered mutational information.
The likelihood of a set of mutations given an ARG $\mathcal{G}$ given mutation rate $\mu$ is
\begin{equation}\label{eq:lik-mut}
    \mathcal{L}(\mathcal{D}|\mathcal{G}, \mu)
    \prod_{e \in E} \frac{(\mu(t_p-t_c)(y-x))^{m_e}}{m_e!} e^{-\mu (t_p-t_c)(y-x)} ,
    % I don't think the following is correct:
    % \frac{1}{\mathcal{M}!} \prod_{(p, c, x, y) \in E} e^{-(y-x)(t_p-t_c)\mu^{|m_e|}}
where 
% $\mathcal{M}$ the total number of mutations and 
$m_e$ is the number of mutations along edge $e$ 
and as before $e = (p,c,x,y)$
\citep{mahmoudi_bayesian_2022}.

>>>>

and not considered mutational information. 
Assuming the infinite sites model, computing the likelihood of 
an ARG given a mutation rate $\mu$ and set of mutations is straightforward, 
as the overall likelihood can be directly decomposed into the per-edge
contributions~\citep{baumdicker_efficient_2021,mahmoudi_bayesian_2022}.

% The likelihood of a set of mutations given an ARG $\mathcal{G}$ given mutation rate $\mu$ is
% \begin{equation}\label{eq:lik-mut}
%     \mathcal{L}(\mathcal{D}|\mathcal{G}, \mu)
%     =
%     \prod_{e \in E} \frac{(\mu(t_p-t_c)(y-x))^{m_e}}{m_e!} e^{-\mu (t_p-t_c)(y-x)} ,
%     % I don't think the following is correct:
%     % \frac{1}{\mathcal{M}!} \prod_{(p, c, x, y) \in E} e^{-(y-x)(t_p-t_c)\mu^{|m_e|}}
% \end{equation}
% where 
% % $\mathcal{M}$ the total number of mutations and 
% $m_e$ is the number of mutations along edge $e$ 
% and as before $e = (p,c,x,y)$
% \citep{mahmoudi_bayesian_2022}.
